Exploratory data analysis

### 2021-03-29 analysis/eda.Rmd
wflow_publish(knitr_in("analysis/eda.Rmd"), view = FALSE, verbose = TRUE)

pca_vi <- DataExplorer::plot_prcomp(vi_data_no_defol_no_response,
  variance_cap = 0.95,
  ggtheme = ggpubr::theme_pubclean(),
  geom_label_args = list(size = 2.5, nudge_y = 0.03),
  parallel = TRUE
)
pca_vi = pca_vi[[1]] +
  labs(title = "Target POV: 95%")
pca_vi[[1]]
```

@@

pca_nri <- DataExplorer::plot_prcomp(nri_data_no_response,
  variance_cap = 0.95,
  ggtheme = ggpubr::theme_pubclean(),
  geom_label_args = list(size = 2.5, nudge_y = 0.03),
  parallel = TRUE
)
pca_nri = pca_nri[[1]] +
  labs(title = "Target POV: 95%")
pca_nri
```

@@

pca_hr <- DataExplorer::plot_prcomp(bands_data_no_response,
  variance_cap = 0.98,
  geom_label_args = list(size = 2.5, nudge_y = 0.03),
  ggtheme = ggpubr::theme_pubclean()
)
pca_hr = pca_hr[[1]] +
  labs(title = "Target POV: 95%")
pca_hr
```

@@

```{r eda-12 }
vi_data_plot <- vi_data %>%
  mutate(plot = factor(rep(
    c("Laukiz 1", "Laukiz 2", "Luiando", "Oiartzun"),
    c(559, 451, 301, 497)
  )))
```

@@

```{r eda-18 }
plots <- list("Laukiz 1", "Laukiz 2", "Luiando", "Oiartzun")
dist <- map(plots, ~ {
  coords <- coords_vi_nri_clean %>%
    mutate(plot = factor(rep(
      c("Laukiz 1", "Laukiz 2", "Luiando", "Oiartzun"),
      c(559, 451, 301, 497)
    ))) %>%
    filter(plot == .x) %>%
    dplyr::select(-plot)
  points <- SpatialPoints(
    coords = coords,
    # EPSG: 25830
    proj4string = CRS("+proj=utm +zone=30 +ellps=WGS84 +datum=WGS84 +units=m +no_defs")
  )
  distance <- mean(as.dist(pointDistance(points,
    allpairs = TRUE,
    lonlat = FALSE
  )))
})
set_names(dist, plots)
dist_plots <- unlist(dist)
```

>>>>

pca_vi <- DataExplorer::plot_prcomp(vi_data_no_defol_no_response,
  variance_cap = 0.95,
  ggtheme = ggpubr::theme_pubclean(),
  geom_label_args = list(size = 2.5, nudge_y = 0.03),
  parallel = TRUE
)
pca_vi <- pca_vi[[1]] +
  labs(title = "Target POV: 95%")
pca_vi[[1]]
```

@@

pca_nri <- DataExplorer::plot_prcomp(nri_data_no_response,
  variance_cap = 0.95,
  ggtheme = ggpubr::theme_pubclean(),
  geom_label_args = list(size = 2.5, nudge_y = 0.03),
  parallel = TRUE
)
pca_nri <- pca_nri[[1]] +
  labs(title = "Target POV: 95%")
pca_nri
```

@@

pca_hr <- DataExplorer::plot_prcomp(bands_data_no_response,
  variance_cap = 0.98,
  geom_label_args = list(size = 2.5, nudge_y = 0.03),
  ggtheme = ggpubr::theme_pubclean()
)
pca_hr <- pca_hr[[1]] +
  labs(title = "Target POV: 95%")
pca_hr
```

@@

```{r eda-12 }
vi_data_plot <- vi_data %>%
  mutate(plot = factor(rep(
    c("Laukiz 1", "Laukiz 2", "Luiando", "Oiartzun"),
    c(479, 451, 300, 529)
  )))
```

@@

```{r eda-18 }
plots <- list("Laukiz 1", "Laukiz 2", "Luiando", "Oiartzun")
dist <- map(plots, ~ {
  coords <- coords_vi_nri_clean %>%
    mutate(plot = factor(rep(
      c("Laukiz 1", "Laukiz 2", "Luiando", "Oiartzun"),
      c(479, 451, 300, 529)
    ))) %>%
    filter(plot == .x) %>%
    dplyr::select(-plot)
  points <- SpatialPoints(
    coords = coords,
    # EPSG: 25830
    proj4string = CRS("+proj=utm +zone=30 +ellps=WGS84 +datum=WGS84 +units=m +no_defs")
  )
  distance <- mean(as.dist(pointDistance(points,
    allpairs = TRUE,
    lonlat = FALSE
  )))
})
set_names(dist, plots)
dist_plots <- unlist(dist)
```
